---
title: 'Reproducible Research: Peer Assessment 1'
author: "Bui Dinh Ngoc"
date: "8 Dec 2015"
output:

  html_document: "PA1_template.html"
  ma
---


## Loading and preprocessing the data
# 1.Load the data (i.e. read.csv()) some lib require here
```{r}

library(readr)
library(data.table)
library(plyr)
library(lattice)

dat = read_csv('activity.zip',na='NA',col_types='dcd')

names(dat)
head(dat)
str(dat)

```
# Process/transform the data (if necessary) into a format suitable for your analysis
# Convert the 2nd column to Date type:   

```{r}
dat$date<-as.Date(dat$date, "%Y-%m-%d")
head(dat)
```

## What is mean total number of steps taken per day?

```{r}
  tidydata<-na.omit(dat)
steps<-aggregate(steps ~ date, tidydata, sum)
hist(steps$steps, main="Total number of steps taken per day", xlab="Steps per Day", col="green")
mean<-mean(steps$steps)
median<-median(steps$steps)
mean
median
  
```


## What is the average daily activity pattern?
```{r}
Interval<-unique(tidydata$interval)
avgStep <- tapply(tidydata$steps, tidydata$interval, mean)
##and plot
plot(Interval,avgStep,type="l",ylab="Average steps", main="Average steps per interval")

maximum <- names(which.max(avgStep))
maximum
```
## Imputing missing values
```{r}
missing <- nrow(dat)-nrow(tidydata)
missing
isna <- is.na(dat)
dat2 <- dat
dat2$steps[which(isna)] <- avgStep[match(dat$interval[which(isna)], dat$interval)]

steps2 <- aggregate(steps ~ date, dat2, sum)
hist(steps2$steps, main="Total number of steps taken per day", xlab="Steps per Day", col="green")

mean <- mean(steps2$steps)
median<- median(steps2$steps)
mean
median

```

## Are there differences in activity patterns between weekdays and weekends?
```{r}



dat2$weekdays <- factor(format(dat2$date, "%A"))
levels(dat2$weekdays)
levels(dat2$weekdays) <- list(weekday = c("Monday", "Tuesday",
                                             "Wednesday", 
                                             "Thursday", "Friday"),
                                 weekend = c("Saturday", "Sunday"))
levels(dat2$weekdays)
table(dat2$weekdays)

avgSteps <- aggregate(dat2$steps, 
                      list(interval = as.numeric(as.character(dat2$interval)), 
                           weekdays = dat2$weekdays),
                      FUN = "mean")
names(avgSteps)[3] <- "meanOfSteps"
library(lattice)
xyplot(avgSteps$meanOfSteps ~ avgSteps$interval | avgSteps$weekdays, 
       layout = c(1, 2), type = "l", 
       xlab = "Interval", ylab = "Number of steps")

```