---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
author: "Bui Dinh Ngoc"
date: "8 Dec 2015"

---


## Loading and preprocessing the data
# 1.Load the data (i.e. read.csv()) some lib require here
```{r}
install.packages("readr")
library(readr)
library(data.table)
library(plyr)
library(lattice)

dat = read_csv('activity.zip',na='NA',col_types='dcd')

names(dat)
head(dat)
str(dat)

```
# Process/transform the data (if necessary) into a format suitable for your analysis
# Convert the 2nd column to Date type:   

```{r}
dat$date<-as.Date(dat$date, "%Y-%m-%d")
head(dat)
```

## What is mean total number of steps taken per day?

```{r}
  tidydata<-na.omit(dat)
steps<-aggregate(steps ~ date, tidydata, sum)
hist(steps$steps, main="Total number of steps taken per day", xlab="Steps per Day", col="green")
mean<-mean(steps$steps)
median<-median(steps$steps)
mean
median
  
```


## What is the average daily activity pattern?
```{r}
Interval<-unique(tidydata$interval)
avgStep <- tapply(tidydata$steps, tidydata$interval, mean)
##and plot
plot(Interval,avgStep,type="l",ylab="Average steps", main="Average steps per interval")

maximum <- names(which.max(avgStep))
maximum
```
## Imputing missing values
```{r}
missing <- nrow(dat)-nrow(tidydata)
missing
isna <- is.na(dat)
dat2 <- dat
dat2$steps[which(isna)] <- avgStep[match(dat$interval[which(isna)], dat$interval)]

steps2 <- aggregate(steps ~ date, dat2, sum)
hist(steps2$steps, main="Total number of steps taken per day", xlab="Steps per Day", col="green")

mean <- mean(steps2$steps)
median<- median(steps2$steps)
mean
median

```

## Are there differences in activity patterns between weekdays and weekends?
```{r}

weekpart = function(x){
        if(x %in% c('Saturday', 'Sunday')){
                return('Weekend')
        }

        return('Weekday')
}
dat2$dayname = weekdays(as.Date(dat2$date))
dat2$daytype  = as.factor(apply(as.matrix(dat2$dayname), 1, weekpart))

dat2
str(dat2)


avgStep2 <- ddply(dat2, .(interval, day), summarize, steps = mean(steps))
xyplot(steps ~ interval | day, data = avgStep2, type = "l", layout = c(1, 2), 
    xlab = "Interval", ylab = "Number of steps", main = "Average steps by day")

```